PhD Title \\ PhD Thesis

### 2024-06-08 Latex_files/Thesis/chapters/chapter 2/main.tex
addressing comments and added figures to chapter 4

These 4 equations describe how the electric and magnetic fields must behave and are also related to one another, any discussion of optical trapping is underpinned by the fact that in all cases the Maxwell Equations must be satisfied.

@@

The Lorenz Mie theory provides an exact solution to the maxwell equations for the scattering caused by an isotropic sphere. The theory describes the scattered wave given off by a dielectric sphere when incident by a plane wave as a summation of partial spherical waves. For any spherical wave the vector fields must solve the Helmholtz wave equation given by:
\begin{align}
	\nabla^2\mathbf{E} +k^2\mathbf{E} = 0
\end{align} 
This combined with the constraints of Maxwell's Equations leaves very few exact solutions apart from spherical or planar waves, both of which can be converted between with relative ease. For example, a plane wave electric field can be expanded into spherical harmonics and likewise any spherical wave can be described as combination of plane waves offset from one another. For a single plane wave the incident, internal, and scattered fields are given as:
\begin{align}
  {\bf E}_{\rm inc}({\bf r})
  &=
    E_0 \sum_{nm}^\infty \left[
    a_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    + b_{nm}{\bf N}_{nm}^{(1)}({\bf r})\right]
  \\
  {\bf E}_{\rm int}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty i^n\frac{2n+1}{n(n+1)}\left[
    -id_{nm}{\bf N}_{nm}^{(1)}({\bf r}) + c_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    \right]
  \\
  {\bf E}_{\rm scat}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty  i^n\frac{2n+1}{n(n+1)}\left[
      -i p_{nm}{\bf N}_{nm}^{(3)}({\bf r})+q_{nm}{\bf M}_{nm}^{(3)}({\bf r})
    \right]
\end{align}
where $a_{nm}$, $b_{nm}$, $c_{nm}$, $d_{nm}$, $p_{nm}$, and $q_{nm}$
are the expansion coefficients of each of the fields, for the incident
field computing its expansion coefficients is possible via analytical
methods and are completely dependent on the beam conditions imposed by
the user.  However, computing the expansion coefficients of the
internal and external fields be far more tedious depending on the
shape of the target and what properties of the scattered field are
desired --- all of which is discussed later on.  From an optical
trapping perspective the force exerted by a focused electric field can
be found by computing the Maxwell stress tensor which only requires
the total magnitude of the incident and scattered fields, essentially
computing the momentum contained in the incident beam and how much of
it has been transferred to the target particle.

@@

\subsection{Finite Difference}
The Finite Difference approach involves discretizing the time and spatial elements in order to approximate the higher order terms. If we assume that $x(t)$ is differentiable to n (we can find its $n^{th}$ derivative) then we can use the Taylor series expansion to get:
\begin{align}
	x(t+\Delta t) = x(t)+\frac{x'(t)}{1!}\Delta t + \frac{x^2(t)}{2!}\Delta t^2+...+\frac{x^n(t)}{n!}\Delta t^n+R_n(x(t))	
\end{align}
Where $R_n(x(t))$ is the remainder term between the Taylor expansion to term n and the actual expression. If we limit our approach to the first derivative only we find that for sufficiently small values of $R_1$ the velocity and acceleration can be approximated as:
\begin{align}
	x'(t) &= \frac{x(t+\Delta t)-x(t)}{\Delta t}=\frac{dx(t))}{dt} \\
	x^2(t) &= \frac{x'(t+\Delta t)-x'(t)}{\Delta t} = \frac{x(t)-2x(t+\Delta t)+x(t+2\Delta t)}{\Delta t^2}
\end{align}
By reversing the time step (i.e. use $-\Delta t$) to approximate the velocity and acceleration based on the previous time steps we can discretize the position by taking finitely small  time steps (i.e. $x(t) = x_i,\ x(t-\Delta t) = x_{i-1}$). The same cannot be done for white noise as no information is known about $W(t)$ at any time. We can instead say that the velocity of a Brownian particle should approximate our white noise as a random walk, where at each new time step the position changes randomly within a given range. Constricting the variance to $\sqrt{2D}/\Delta t$ allows us to represent the white noise using the finite-difference approach as:
\begin{align}
	m\frac{x_i-2x_{i-1}+x_{i-2}}{\Delta t^2} = -\gamma\frac{x_i-x_{i-1}}{\Delta t}+\sqrt{2k_BT\gamma}\frac{w_i}{\sqrt{\Delta t}}
\end{align}
Where $w_i$ is a random real number between -1 and 1, we can say that it is normally distributed around 0 for simulation purposes. We can rearrange this for $x_i$ to approximate the Brownian motion of a particle (setting $x_0=0$), where the characteristic time is $\tau = m/\gamma$. Now in the case of an optical trap the restoration time scale is given by $\tau_{OT}=\kappa_x/\gamma$ which for strongly trapped particles is far greater than the characteristic time, therefore for simulation purposes we can neglect the particle's inertia which allows us to write the motion of an optically trapped particle as:
\begin{align}
	\label{eq:sim_langevin}
	x_i = x_{i-1} + \tau_{OT}\ x_{i-1}\Delta t + \sqrt{2D\Delta t}\ w_i
\end{align}

@@

\subsection{Equipartition method}
The Equipartition method is by far the fastest and simplest means for estimating the trap strength but unlike Potential Analysis is limited strictly to harmonic potentials. This can be often not the case for highly focused beams, as the trap strength can vary due to polarisation differences. Simply put we can use the equipartition theorem to relate the potential well to the particle's thermal energy using eq.~\ref{eq:prob_dist}:
\begin{align}
	\left<U(x)\right> = \frac{1}{2}\kappa\left<(x-x_{eq})^2\right> &= \int_{-\infty}^{\infty}\rho(x)(x-x_{eq})^2 = \frac{1}{2}k_BT \\
	\implies \kappa_x &= \frac{k_BT}{\left<(x-x_{eq})^2\right>} 
\end{align}

@@

Later chapters cover the dynamics of spherical aggregates and anisotropic scatterers, these subjects are particularly difficult to characterise using conventional calibration techniques \cite{Li2008, Yogesha2011PreciseCO}. As an example consider a symmetric dimer as a paradigmatic aggregate; if we consider the Langevin equation for such a aggregate within an optical trap we have:
\begin{align}
\frac{{d}\vec{r}(t)}{{dt}} = \frac{\vec{\kappa}_x}{\gamma}\vec{r}(t) + \sqrt{2\vec{D}_x}\eta(t)
\end{align}
Where $x(t)$ is replaced with $\vec{r}(t)$ to signify that the translational motion is generalised to a 3 dimensional case. Except now, the dimer is undergoing random rotational motion in addition to its Brownian translational motion the first term on the right hand side is no longer purely a function of the dimer's position but also on its orientation. The rotational form of the Langevin equation for a dipole within an external potential is given as:
\begin{align}
  \frac{{d}\vec{u}(t)}{{dt}}
  =
  \frac{\mu}{\gamma_R}\left[\vec{u}(t)\times E(t)\right]\times \vec{u}(t)
  + \sqrt{2\vec{D}_R}\lambda(t)\times \vec{u}(t)
\end{align}
Where $\vec{u}(t)$ is the unit vector aligned along the centres of the two spheres, $\mu$ is its dipole moment, and $\gamma_R$ is the rotational friction coefficient which is given as $\gamma_R = 8\pi\eta r^3$, if the dimer is within a harmonic potential we can write the first term on the right hand side as $\frac{\vec{\kappa}_u}{\gamma} \times \vec{u}(t)$, where $\vec{\kappa}_u$ is the rotational stiffness vector. $\lambda(t)$ is the Brownian rotations from the surrounding fluid, like in the translational case the Brownian rotations are normally distributed and are also uncorrelated so that:
\begin{align}
  \left<\lambda(t)\lambda(t')\right> = \delta_{ij}\delta(t-t')
\end{align}
For an asymmetric scatterer whose radius is comparable to that of the electric field's wavelength we now have a system of simultaneous equations:
\begin{align}
	\label{eq:full_langevin}
  \frac{{d}\vec{r}(t)}{{dt}}
  &=
    \frac{\vec{\kappa}_x(\vec{u}(t))}{\gamma}\vec{r}(t) + \sqrt{2D}\eta(t)
  \\
  \frac{{d}\vec{u}(t)}{{dt}}
  &=
    \frac{\vec{\kappa}_u(\vec{r}(t))}{\gamma_R}\times \vec{u}(t)
    + \sqrt{2\vec{D}_R}\lambda(t)\times \vec{u}(t)
\end{align}
Fortunately, we do not need to solve these directly as the latter two
random variables can be easily approximated if the thermal energy of
the system is know, and the rate of change can be assumed as linear if
we take a sufficiently small time step that
$\Delta t~\ll~\kappa_x/\gamma \ \& \ \Delta t \ll
\kappa_u/\gamma_R$. In doing so we now only need to compute the
optical force and torque applied to our dimer, this has already been
compiled in a MATLAB package called \textit{Optical Tweezer Toolbox}
or \textit{ott} \cite{Nieminen2007}. In which they use the results
from \cite{Farsund1996} to compute both the optical force and torque
using the beam coefficients - the form given by
\cite{Crichton2000THEMD} is an easier form to compute:
\begin{equation}
\begin{split}
  \bold{F_z}
  &=
    -\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{n,m}b*_{n,m}-p_{n,m}q*_{n,m}] \right.
  \\ 
  &+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left. \times \Im[b_{n,m}b*_{n,m}+a_{n,m}a*_{n+1,m} - q_{n,m}q*_{n,m}+p_{n,m}p*_{n+1,m}] \right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
  \bold{T_z}
  &=
    -\frac{1}{8\pi k^3}\sum_{n,m} \left(\frac{m}{n(n+1)}[|a_{n,m}|^2+|b_{n,m}|^2-|p_{n,m}|^2-|q_{n,m}|^2] \right.
  \\ 
  &+\frac{2}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left. \times \Re[b_{n,m}a*_{n,m}+a_{n,m}b*_{n+1,m} - p_{n,m}q*_{n,m}+q_{n,m}p*_{n+1,m}] \right)
\end{split}
\end{equation}
where $a_{nm}$, $b_{nm}$, $p_{nm}$, and $q_{nm}$ are the beam coefficients of the incident and scattered fields respectively. We can get the transverse force and torque components in a similar form by applying a simple rotation transformation. In order to get the scattered beam coefficients we can use \textit{MSTM} \cite{Mackowski2011} to calculate the T-matrix of our dimer (or any spherical aggregate). Vigilante et al compiled together a python package that combines both \textit{ott} and \textit{MSTM} to simulate the behaviour of spherical aggregates within a predefined optical trap.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{./figs/fixed_polarisation.png}
\end{figure}

>>>>

These 4 equations describe how the electric and magnetic fields behave and are related to one another at a microscopic level. Any discussion of optical trapping is underpinned by the fact that in all cases the Maxwell Equations must be satisfied at the macroscopic level, where one must account for the medium's interactions with the EM field. Macroscopic forms of the maxwell equations are given below \cite{Jackson_1975}:
\begin{align}
	\nabla \cdot \mathbf{D}
	&= \rho_f
	\\
	\nabla \cdot \mathbf{B}
	&= 0
	\\
	\nabla \times \mathbf{E}
	&= \frac{\partial \mathbf{B}}{\partial t}
	\\
	\nabla \times \mathbf{H}
	&= \mathbf{J}_f +\frac{\partial \mathbf{D}}{\partial t}  
\end{align}
Where $\rho_f$ and $\mathbf{J}_f$ are the charge density and current caused by the presence of free charges in the medium, and $\mathbf{D}$ and $\mathbf{H}$ are the displacement and magnetizing fields respectively. The latter two are defined by:
\begin{align}
	\nonumber
	\mathbf{D} &= \epsilon_0\mathbf{E}+\mathbf{P} 
	\\ 
	\nonumber
	\mathbf{H} &= \frac{1}{\mu_0}\mathbf{B}-\mathbf{M}
\end{align}
Where $\mathbf{P}$ is the polarization field and $\mathbf{M}$ is the magnetisation field, these fields arise due to the bound charges throughout the medium interacting with the EM field.

@@

The Lorenz Mie theory provides an exact solution to the maxwell equations for the scattering caused by an isotropic sphere. The theory describes the scattered wave given off by a dielectric sphere when incident by a plane wave as a summation of partial spherical waves. For any spherical wave the vector fields must solve the Helmholtz wave equation given by:
\begin{align}
	\nabla^2\mathbf{E} +k^2\mathbf{E} = 0
\end{align} 
Where $k$ is the wave number of the electromagnetic radiation ($k = 2\pi/\lambda$) This combined with the constraints of Maxwell's Equations leaves very few exact solutions apart from spherical or planar waves, both of which can be converted between with relative ease. For example, a plane wave electric field can be expanded into spherical harmonics and likewise any spherical wave can be described as combination of plane waves offset from one another. For a single plane wave the incident, internal, and scattered fields are given as:
\begin{align}
  {\bf E}_{\rm inc}({\bf r})
  &=
    E_0 \sum_{nm}^\infty \left[
    a_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    + b_{nm}{\bf N}_{nm}^{(1)}({\bf r})\right]
  \\
  {\bf E}_{\rm int}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty i^n\frac{2n+1}{n(n+1)}\left[
    -id_{nm}{\bf N}_{nm}^{(1)}({\bf r}) + c_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    \right]
  \\
  {\bf E}_{\rm scat}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty  i^n\frac{2n+1}{n(n+1)}\left[
      -i p_{nm}{\bf N}_{nm}^{(3)}({\bf r})+q_{nm}{\bf M}_{nm}^{(3)}({\bf r})
    \right] 
    \\
	\mathbf{E}_{tot}({\bf r}) &= 
	\begin{cases}
		{\bf E}_{\rm inc}({\bf r}) + {\bf E}_{\rm scat}({\bf r}) & \text{if \textbf{r} outside}
		\\ 
		{\bf E}_{\rm int}({\bf r}) & \text{if \textbf{r} inside}
	\end{cases}
\end{align}
where $a_{nm}$, $b_{nm}$, $c_{nm}$, $d_{nm}$, $p_{nm}$, and $q_{nm}$
are the expansion coefficients of each of the fields, for the incident
field computing its expansion coefficients is possible via analytical
methods and are completely dependent on the beam conditions imposed by
the user.  However, computing the expansion coefficients of the
internal and external fields be far more tedious depending on the
shape of the target and what properties of the scattered field are
desired --- all of which is discussed later on.  From an optical
trapping perspective the force exerted by a focused electric field can
be found by computing the Maxwell stress tensor which only requires
the total magnitude of the incident and scattered fields, essentially
computing the momentum contained in the incident beam and how much of
it has been transferred to the target particle.

@@

\subsection{Finite Difference}
The Finite Difference approach involves discretizing the time and spatial elements in order to approximate the higher order terms. If we assume that $x(t)$ is differentiable to n (we can find its $n^{th}$ derivative) then we can use the Taylor series expansion to get:
\begin{align}
	x(t+\Delta t) = x(t)+\frac{x'(t)}{1!}\Delta t + \frac{x^2(t)}{2!}\Delta t^2+...+\frac{x^n(t)}{n!}\Delta t^n+R_n(x(t))	
\end{align}
Where $R_n(x(t))$ is the remainder term between the Taylor expansion to term n and the actual expression. If we limit our approach to the first derivative only we find that for sufficiently small values of $R_1$ the velocity and acceleration can be approximated as:
\begin{align}
	x'(t) &\approx \frac{x(t+\Delta t)-x(t)}{\Delta t}
	\\
	x^{''}(t) &\approx \frac{x'(t+\Delta t)-x'(t)}{\Delta t} = \frac{x(t)-2x(t+\Delta t)+x(t+2\Delta t)}{\Delta t^2}
\end{align}
By reversing the time step (i.e. use $-\Delta t$) to approximate the velocity and acceleration based on the previous time steps we can discretize the position by taking finitely small  time steps (i.e. $x(t) = x_i,\ x(t-\Delta t) = x_{i-1}$). The same cannot be done for white noise as no information is known about $W(t)$ at any time. We can instead say that the velocity of a Brownian particle should approximate our white noise as a random walk, where at each new time step the position changes randomly within a given range. Constricting the variance to $\sqrt{2D}/\Delta t$ allows us to represent the white noise using the finite-difference approach as:
\begin{align}
	m\frac{x_i-2x_{i-1}+x_{i-2}}{\Delta t^2} = -\gamma\frac{x_i-x_{i-1}}{\Delta t}+\sqrt{2k_BT\gamma}\frac{w_i}{\sqrt{\Delta t}}
\end{align}
Where $w_i$ is a random real number between -1 and 1, we can say that it is normally distributed around 0 for simulation purposes. We can rearrange this for $x_i$ to approximate the Brownian motion of a particle (setting $x_0=0$), where the characteristic time is $\tau = m/\gamma$. Now in the case of an optical trap the restoration time scale is given by $\tau_{OT}=\kappa_x/\gamma$ which for strongly trapped particles is far greater than the characteristic time, therefore for simulation purposes we can neglect the particle's inertia which allows us to write the motion of an optically trapped particle as:
\begin{align}
	\label{eq:sim_langevin}
	x_i = x_{i-1} + \tau_{OT}\ x_{i-1}\Delta t + \sqrt{2D\Delta t}\ w_i
\end{align}

@@

\subsection{Equipartition method}
The Equipartition method is by far the fastest and simplest means for estimating the trap strength but unlike Potential Analysis is limited strictly to harmonic potentials. This can be often not the case for highly focused beams, as the trap strength can vary due to polarisation differences. Simply put we can use the equipartition theorem to relate the potential well to the particle's thermal energy using eq.~\ref{eq:prob_dist}:
\begin{align}
	\left<U(x)\right> = \frac{1}{2}\kappa_x\left<(x-x_{eq})^2\right> &= \int_{-\infty}^{\infty}\rho(x)(x-x_{eq})^2 = \frac{1}{2}k_BT \\
	\implies \kappa_x &= \frac{k_BT}{\left<(x-x_{eq})^2\right>} 
\end{align}

@@

Later chapters cover the dynamics of spherical aggregates and anisotropic scatterers, these subjects are particularly difficult to characterise using conventional calibration techniques \cite{Li2008, Yogesha2011PreciseCO}. As an example consider a symmetric dimer as a paradigmatic aggregate; if we consider the Langevin equation for such a aggregate within an optical trap we have:
\begin{align}
\frac{{d}\vec{r}(t)}{{dt}} = \frac{\vec{\kappa}_x}{\gamma}\vec{r}(t) + \sqrt{2\vec{D}_x}\eta(t)
\end{align}
Where $x(t)$ is replaced with $\vec{r}(t)$ to signify that the translational motion is generalised to a 3 dimensional case. Except now, the dimer is undergoing random rotational motion in addition to its Brownian translational motion the first term on the right hand side is no longer purely a function of the dimer's position but also on its orientation. The rotational form of the Langevin equation for a dipole within an external potential is given as:
\begin{align}
  \frac{{d}\vec{u}(t)}{{dt}}
  =
  \frac{\mu}{\gamma_R}\left[\vec{u}(t)\times E(t)\right]\times \vec{u}(t)
  + \sqrt{2\vec{D}_R}\lambda(t)\times \vec{u}(t)
\end{align}
Where $\vec{u}(t)$ is the unit vector aligned along the centres of the two spheres, $\mu$ is its dipole moment, and $\gamma_R$ is the rotational friction coefficient which is given as $\gamma_R = 8\pi\eta r^3$, if the dimer is within a harmonic potential we can write the first term on the right hand side as $\frac{\vec{\kappa}_u}{\gamma} \times \vec{u}(t)$, where $\vec{\kappa}_u$ is the rotational stiffness vector. $\lambda(t)$ is the Brownian rotations from the surrounding fluid, like in the translational case the Brownian rotations are normally distributed and are also uncorrelated so that:
\begin{align}
  \left<\lambda(t)\lambda(t')\right> = \delta_{ij}\delta(t-t')
\end{align}
For an asymmetric scatterer whose radius is comparable to that of the electric field's wavelength we now have a system of simultaneous equations:
\begin{align}
	\label{eq:full_langevin}
  \frac{{d}\vec{r}(t)}{{dt}}
  &=
    \frac{\vec{\kappa}_x(\vec{u}(t))}{\gamma}\vec{r}(t) + \sqrt{2D}\eta(t)
  \\
  \frac{{d}\vec{u}(t)}{{dt}}
  &=
    \frac{\vec{\kappa}_u(\vec{r}(t))}{\gamma_R}\times \vec{u}(t)
    + \sqrt{2\vec{D}_R}\lambda(t)\times \vec{u}(t)
\end{align}
Fortunately, we do not need to solve these directly as the latter two
random variables can be easily approximated if the thermal energy of
the system is know, and the rate of change can be assumed as linear if
we take a sufficiently small time step that
$\Delta t~\ll~\kappa_x/\gamma \ \& \ \Delta t \ll
\kappa_u/\gamma_R$. In doing so we now only need to compute the
optical force and torque applied to our dimer, this has already been
compiled in a MATLAB package called \textit{Optical Tweezer Toolbox}
or \textit{ott} \cite{Nieminen2007}. In which they use the results
from \cite{Farsund1996} to compute both the optical force and torque
using the beam coefficients - the form given by
\cite{Crichton2000THEMD} is an easier form to compute:

\begin{equation}
\begin{split}
  \bold{F_z}
  &=
    -\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}-p_{nm}q^*_{nm}] \right.
  \\ 
  &+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}-q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
  \bold{T_z}
  &=
    -\frac{1}{8\pi k^3}\sum_{n,m} \left(\frac{m}{n(n+1)}[|a_{nm}|^2+|b_{nm}|^2-|p_{nm}|^2-|q_{nm}|^2] \right.
  \\ 
  &+\frac{2}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Re[b_{nm}a^*_{nm}+a_{nm}b^*_{n+1m}-p_{nm}q^*_{nm}+q_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}
where $a_{nm}$, $b_{nm}$, $p_{nm}$, and $q_{nm}$ are the beam coefficients of the incident and scattered fields respectively. We can get the transverse force and torque components in a similar form by applying a simple rotation transformation. In order to get the scattered beam coefficients we can use \textit{MSTM} \cite{Mackowski2011} to calculate the T-matrix of our dimer (or any spherical aggregate). Vigilante et al compiled together a python package that combines both \textit{ott} and \textit{MSTM} to simulate the behaviour of spherical aggregates within a predefined optical trap.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{fixed_polarisation.png}
\end{figure}

### 2024-06-08 Latex_files/Thesis/chapters/chapter 4/main.tex
addressing comments and added figures to chapter 4

\chapter{Complex Langevin dynamics of simple spherical aggregates}

\comment{Do you actually examine aggregates larger than dimers?  If
  not, then just change the title to reflect that you just examine dimers.}

Much of the calibration theory discussed in Chapter 2 assumes that the target particle in question is a single sphere, one who's scattering and motion is easily computed. However, while working with dense colloidal suspensions, one often ends up trapping more than one sphere. Li and Arlt \cite{Li2008} studied the case of two microspheres trapped in a single OT and found that multiple trapped beads could be mistaken for a single trapped bead with altered trap stiffness. Theoretical studies on the case of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a ray-optics based model to show that the two trapped beads are brought into physical contact with each other by optical forces and they also calculated the axial equilibrium positions of the two trapped beads as a function of their size. Experiments in \cite{Praveen2016} confirmed that the two trapped beads indeed experience different trap stiffnesses in the vicinity of the same potential well. There are further discussions looking into the dynamics of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, Chetana2022}, their results all showing that predicting the behaviour an arbitrary shaped particle comes with great difficulty due to the fact that the optical force is dependent on a greater number of variables such as orientation and size factors.

@@

These results are somewhat contrary to other work with silica dimers
\cite{Ahn2018, Debuysschere2023,Reimann2018}; previous experiments
have trapped the dimer in an orientation perpendicular to the beam
propagation direction.  The rotational motion is induced due to the
asymmetric geometry creating an unbalanced polarisation susceptibility
along its long axis as compared to its short axis; therefore its long
axis is aligned with the polarisation vector and can rotate
freely\cite{Ahn2018}.  This however cannot be the case with our
simulations as the dimer rotates about its long axis, meaning there
cannot be an asymmetric axis to align with the beam's polarisation
vector. Furthermore, we see a non-linear increase in the rotational
speed of our dimers with size, the drag torque from the surrounding
fluid is $\propto r^3$ so the expectation is that the rotation
frequency should fall off with increasing size.  This indicates that
the rotational motion is due to the shape asymmetry of the dimer and
not solely due to the beam's angular momentum.  Measurement of this
photo-kinetic force is difficult to achieve due to the fact that
previous analysis was conducted in the Rayleigh regime, where the
polarizability of our dimer can be approximated as:
\begin{align}
  \bold{p}({\bf r},t)
  =
  \alpha_x E_x({\bf r},t)\hat{\bf e}_x
  + \alpha_yE_y({\bf r},t)\hat{\bf e}_y
  + \alpha_zE_z({\bf r},t)\hat{\bf e}_z
\end{align}
where the polarizability is given as a 3D vector for the three
principle Cartesian directions.  In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer.

>>>>

\chapter{Complex Langevin dynamics of spherical dimers}

\comment{Do you actually examine aggregates larger than dimers?  If
  not, then just change the title to reflect that you just examine dimers.}
Much of the calibration theory discussed in Chapter 2 assumes that the target particle in question is a single sphere, one who's scattering and motion is easily computed. However, while working with dense colloidal suspensions, one often ends up trapping more than one sphere. Li and Arlt \cite{Li2008} studied the case of two microspheres trapped in a single OT and found that multiple trapped beads could be mistaken for a single trapped bead with altered trap stiffness. Theoretical studies on the case of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a ray-optics based model to show that the two trapped beads are brought into physical contact with each other by optical forces and they also calculated the axial equilibrium positions of the two trapped beads as a function of their size. Experiments in \cite{Praveen2016} confirmed that the two trapped beads indeed experience different trap stiffnesses in the vicinity of the same potential well. There are further discussions looking into the dynamics of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, Chetana2022}, their results all showing that predicting the behaviour an arbitrary shaped particle comes with great difficulty due to the fact that the optical force is dependent on a greater number of variables such as orientation and size factors.

@@

These results are somewhat contrary to other work with silica dimers
\cite{Ahn2018, Debuysschere2023,Reimann2018}; previous experiments
have trapped the dimer in an orientation perpendicular to the beam
propagation direction.  The rotational motion is induced due to the
asymmetric geometry creating an unbalanced polarisation susceptibility
along its long axis as compared to its short axis; therefore its long
axis is aligned with the polarisation vector and can rotate
freely\cite{Ahn2018}.  This however cannot be the case with our
simulations as the dimer rotates about its long axis, meaning there
cannot be an asymmetric axis to align with the beam's polarisation
vector. Furthermore, we see a non-linear increase in the rotational
speed of our dimers with size, the drag torque from the surrounding
fluid is $\propto r^3$ so the expectation is that the rotation
frequency should fall off with increasing size.  This indicates that
the rotational motion is due to the shape asymmetry of the dimer and
not solely due to the beam's angular momentum.  Measurement of this
photo-kinetic force is difficult to achieve due to the fact that
previous analysis was conducted in the Rayleigh regime, where the
polarizability of our dimer can be approximated as:
\begin{align}
  \bold{p}({\bf r},t)
  =
  \alpha_x E_x({\bf r},t)\hat{\bf e}_x
  + \alpha_yE_y({\bf r},t)\hat{\bf e}_y
  + \alpha_zE_z({\bf r},t)\hat{\bf e}_z
\end{align}
where the polarizability is given as a 3D vector for the three
principle Cartesian directions.  In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer. Measuring the optical torque 
makes it clear that the polarizability is a contributing factor to this optical 
rotation phenomena. Rotating a symmetric dimer in the $x-z$ plane reveals 
that while the dimer can be rotated in an orientation perpendicular 
to the beam rotational torque is maximised when rotated while aligned with 
the optical axis.

\begin{figure}[t]
	\begin{subfigure}{\linewidth}
	\centering
	\includegraphics[width=0.6\linewidth]{tx_different_polarisations.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
	\includegraphics[width=0.6\linewidth]{ty_different_polarisations.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
	\includegraphics[width=0.6\linewidth]{tz_different_polarisations.png}
	\end{subfigure}
\caption{Calculation of the optical torque about the three primary axis on a symmetric dimer in linear, elliptical, and circular polarisation beams.}
\end{figure}
\newpage
